Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-25 paper/ms.tex
Microtype
breaklinks
Remove weird lines in citation
Rushed abstract edit

\documentclass[12pt, preprint]{aastex}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers

@@

\begin{abstract}
We introduce a probabilistic (Bayesian) method for producing catalogs
from images of crowded stellar fields. The method is capable of handling the
challenges introduced by overlapping sources and is able to determine the luminosity
function of the stars even when the precise luminosity of each star is uncertain.
This is in contrast with standard techniques which produce a single catalog,
potentially underestimating the uncertainties in any study of the stellar
population. The method is implemented using advanced Markov Chain Monte Carlo
(MCMC) techniques including Reversible Jump and Nested Sampling.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainties. We compare the results obtained from our method
with those obtained from the \sex~software and find that the latter significantly
underestimates the number of stars in the image and leads to incorrect
inferences about the luminosity function of the stars.
\end{abstract}

@@

\bibitem[Zhang et al.(2009)]{2009PASP..121.1429Z} Zhang, Z.-W., Kim, D.-W., 
Wang, J.-H., et al.\ 2009, \pasp, 121, 1429 
\end{thebibliography}

>>>>

\documentclass[12pt, preprint]{aastex}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers
\usepackage[breaklinks]{hyperref}

@@

\begin{abstract}
We introduce a probabilistic (Bayesian) method for producing catalogs
from images of crowded stellar fields. The method is capable of inferring the
number of sources $N$ in the image and can also handle the
challenges introduced by overlapping sources. The luminosity
function of the stars can also be inferred even when the precise luminosity of each star is uncertain.
This is in contrast with standard techniques which produce a single catalog,
potentially underestimating the uncertainties in any study of the stellar
population and discarding information about sources at or below the detection limit. The method is implemented using advanced Markov Chain Monte Carlo
(MCMC) techniques including Reversible Jump and Nested Sampling.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. The parameters of the luminosity function can be recovered
with moderate uncertainties. We compare the results obtained from our method
with those obtained from the \sex~software and find that the latter significantly
underestimates the number of stars in the image and leads to incorrect
inferences about the luminosity function of the stars.
\end{abstract}

@@

\bibitem[Zhang et al.(2009)]{2009PASP..121.1429Z} Zhang, Z.~W., Kim, D.~W., 
Wang, J.~H., et al.\ 2009, \pasp, 121, 1429 
\end{thebibliography}
